brados: declarative, programmable object storage

### 2016-05-25 paper.tex
Adds some refs on declarative languages

>>>>

{\bf Declarative Specifications.}
Declarative interfaces have been used for specifying distributed analytic 
tasks~\cite{olston_pig_2008,thusoo_hive_2010}, information 
extraction~\cite{shen_declarative_2007} and distributed 
systems~\cite{conway_logic_2012,bauer_legion_2014}. The use of declarative 
specifications has also been explored in other contexts such as cloud recovery 
testing~\cite{gunawi_fate_2011}, bug reproduction~\cite{li_reprolite_2014} and 
cloud resource orchestration~\cite{liu_declarative_2011}.
